Fast and optimal centroiding of faint stars

### 2015-07-15 ms/figure.tex
Update figure.tex

Moreover, it is more convenient to work with the signal-to-noise ratio
(hereafter denoted by SNR) instead of the variance of the Gaussian noise.
We use the definition of SNR according to which, SNR is given by the ratio
 of the mean and variance of the distribution
which the flux estimator is drawn from. Assume that the total flux from
the point source is $F$, and that the sub-pixel shifted PSF at the $i$-th pixel is given
by $P_{i}$. Therefore the brightness of the $i$-th pixel $y_{i}$ is drawn from
a Gaussian distribution 
\beq
p(y_{i}) = \mathcal{N}(FP_{i},\sigma^{2}). 
\eeq

The optimal estimator of flux is 
the matched filter flux estimator $\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
\beq
p(\tilde{F}) = \mathcal{N}(F , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
\eeq  
which leads us to
\beq
\begin{array}{l}
\text{SNR} = \frac{F\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
\end{array}
\label{snr}
\eeq

@@

We perform two sets of simulations. In the first set, we choose four values of
2, 2.8, 4, and 5.6 pixels for $\gamma$. For each $\gamma$, we generate 100,000 
17 $\times$ 17 postage-stamps of Moffat profiles with centroids randomly drawn
within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, Gaussian
noise is added to each postage-stamp such that the simulated stars are uniformly
 distributed in log-SNR between SNR = 5 to SNR = 100.

In the second set, we generate 100,000 17$\times$17 postage-stamps
of Moffat profile, with values of $\gamma$ uniformly distributed 
between 2 and 6 pixels, and with centroids drawn randomly within 
the central pixel. We choose four values for SNR: 5, 10, 20, and 40. 
For each SNR, and for each postage-stamp with a given $\gamma$, 
Gaussian noise, with variance corresponding to SNR and $\gamma$ through equation 
(\ref{snr2}), is added to each postage-stamp.

>>>>

Moreover, it is more convenient to work with the signal-to-noise ratio
(hereafter denoted by SNR) instead of the variance of the Gaussian noise.
We use the definition of SNR according to which, SNR is given by the ratio
 of the mean and variance of the distribution
which the flux estimator is drawn from. Assuming that the total flux from
the point source is $F$, and that the sub-pixel shifted PSF at the $i$-th pixel is given
by $P_{i}$. Therefore the brightness of the $i$-th pixel $y_{i}$ is drawn from
a Gaussian distribution 
\beq
p(y_{i}) = \mathcal{N}(FP_{i},\sigma^{2}). 
\eeq

The optimal estimator of flux is the matched-filter flux estimator 
$\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
\beq
p(\tilde{F}) = \mathcal{N}(F , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
\eeq  
which leads us to
\beq
\begin{array}{l}
\text{SNR} = \frac{F\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
\end{array}
\label{snr}
\eeq

@@

We perform two sets of simulations. In the first set, we choose four values of
2, 2.8, 4, and 5.6 pixels for $\gamma$. For each $\gamma$, we generate 100,000 
17 $\times$ 17 postage-stamps of Moffat profiles with centroids randomly drawn
within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, zero-mean 
uncorrelated Gaussian noise is added to each postage-stamp such that the simulated 
stars are uniformly distributed in log-SNR between SNR = 5 to SNR = 100.

In the second set, we generate 100,000 17$\times$17 postage-stamps
of Moffat profile, with values of $\gamma$ uniformly distributed 
between 2 and 6 pixels, and with centroids drawn randomly within 
the central pixel. We choose four values for SNR: 5, 10, 20, and 40. 
For each SNR, and for each postage-stamp with a given $\gamma$, 
zero-mean uncorrelated Gaussian noise, with standard deviation corresponding 
to SNR and $\gamma$ through equation (\ref{snr2}), is added to each postage-stamp.
